\documentclass[9pt]{extarticle}
\usepackage[margin=0.75in, headheight=14pt]{geometry}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{titlesec}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\titlespacing*{\section}{0pt}{8pt}{3pt}
\titlespacing*{\subsection}{1.5em}{6pt}{2pt}
\setlist[itemize]{leftmargin=1.5em, nosep}
\setlist[enumerate]{leftmargin=1.5em, nosep}

\title{\vspace{-1.2cm}\huge\textbf{A3: Part 3 to Part 4}\vspace{-0.5em}}
\author{\normalsize Autobook}
\date{\vspace{-1.5em}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small A3: Part 3 to Part 4}
\fancyhead[R]{\small Autobook}
\fancyfoot[C]{\small \thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\lstset{
  basicstyle=\ttfamily\small,
  backgroundcolor=\color{gray!10},
  frame=single,
  framerule=0pt,
  breaklines=true,
  xleftmargin=8pt,
  xrightmargin=8pt,
  aboveskip=4pt,
  belowskip=4pt,
  language=Python,
}

\begin{document}
\maketitle
\thispagestyle{fancy}

P3 produces the picochat checkpoints and metrics that P4 needs for scaling law prediction and emergent abilities comparison.

\leftskip=0pt
\section*{1. Picochat Config}
\leftskip=1.5em

\begin{tabular}{@{}ll@{}}
\toprule
Field & Value \\
\midrule
Depth & 6 \\
Model dim & 384 \\
Attention heads & 3 \\
Total parameters & ${\sim}136$M \\
Scaling parameters & ${\sim}35.8$M \\
Short seq\_len (Stage 1) & 512 \\
Extended seq\_len (Stage 2) & 2048 \\
Nanochat branch/tag & \texttt{baseline-v0} \\
\bottomrule
\end{tabular}

\leftskip=0pt
\section*{2. Checkpoints}
\leftskip=1.5em

Three final checkpoints from P3's three training stages:

\begin{tabular}{@{}llrlrl@{}}
\toprule
Checkpoint & Model tag & Step & How trained & seq\_len & Val BPB \\
\midrule
Short & \texttt{pico-short} & 1433 & From scratch, seq\_len=512 & 512 & 1.0586 \\
Extended & \texttt{pico-short} & 1933 & Resumed from Short, seq\_len=2048, +500 steps & 2048 & 1.0540 \\
Full & \texttt{pico-full} & 1433 & From scratch, seq\_len=2048 & 2048 & 1.0499 \\
\bottomrule
\end{tabular}

\medskip
\textbf{Recommended for P4}: \texttt{pico-full} @ step 1433 --- strongest picochat model (best BPB and CORE).

\subsection*{All available checkpoints}
\leftskip=3em

P3 saved checkpoints every 50 steps. Each step has three files: \texttt{model\_*.pt} (weights), \texttt{optim\_*\_rank0.pt} (optimizer state, only needed to resume training), \texttt{meta\_*.json} (metadata).

\begin{itemize}
  \item \textbf{pico-short} (39 checkpoints): Steps 50--1433 at seq\_len=512 (Stage~1), steps 1450--1933 at seq\_len=2048 (Stage~2)
  \item \textbf{pico-full} (29 checkpoints): Steps 50--1433 at seq\_len=2048 (Stage~3)
\end{itemize}

The checkpoints are on a personal Modal workspace. Ask Seonghyun for any checkpoint you need --- he will download and share it.

\leftskip=0pt
\section*{3. Key Metrics}
\leftskip=1.5em

\begin{tabular}{@{}lccc@{}}
\toprule
Metric & Short (1433) & Extended (1933) & Full (1433) \\
\midrule
Val BPB & 1.0586 & 1.0540 & 1.0499 \\
PG19 Aggregate CE & 4.4029 & 4.2980 & 4.0500 \\
PG19 Aggregate PPL & 81.69 & 73.55 & 57.40 \\
CORE & N/A & 0.0766 & 0.0789 \\
\bottomrule
\end{tabular}

\leftskip=0pt
\section*{4. Cost}
\leftskip=1.5em

\begin{tabular}{@{}ll@{}}
\toprule
Field & Value \\
\midrule
GPU type & A100-80GB \\
Total GPU-hours & 4.67 \\
Estimated cost & \$29.77 \\
\bottomrule
\end{tabular}

\leftskip=0pt
\section*{5. W\&B Runs}
\leftskip=1.5em

\begin{itemize}
  \item \textbf{p3-baseline-short}: \url{https://wandb.ai/seonghyun-ban-uoft/490-autobook-a3/runs/mpaiemt0}
  \item \textbf{p3-baseline-extended}: \url{https://wandb.ai/seonghyun-ban-uoft/490-autobook-a3/runs/woxwtud7}
  \item \textbf{p3-baseline-full}: \url{https://wandb.ai/seonghyun-ban-uoft/490-autobook-a3/runs/wy8sw0zf}
\end{itemize}

W\&B project: \texttt{490-autobook-a3}

\leftskip=0pt
\section*{6. What P4 Needs This For}
\leftskip=1.5em

\subsection*{Scaling Law Prediction}
\leftskip=3em
Use picochat scaling param count (35.8M) + val\_bpb (1.0499 for full, or 1.0540 for extended) to predict nanochat (depth=20) performance. Compare predicted vs actual after P4 training.

\leftskip=1.5em
\subsection*{Emergent Abilities Comparison}
\leftskip=3em
Find 10 questions nanochat answers but picochat cannot. Use the \texttt{pico-full} checkpoint as the ``smaller model'' baseline.

\end{document}
